### 2024-05-01 Tables/MD_noMD_readmort_decomp_fullsample.tex
Update tables AGAIN

\begin{table}[htbp]
   \caption{\label{tab:MD_noMD_readmort_decomp_fullsample} Decomposition of Readmission and Mortality Results for Nonprofits}
   \bigskip
   \centering
   \begin{tabular}{lcccc}
      \toprule
       & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate}\\
                                       & (1)           & (2)           & (3)           & (4)\\  
      \midrule 
      Ever MD Executive x Post Penalty & -0.03         &               & -0.02         &   \\   
                                       & (0.07)        &               & (0.07)        &   \\   
      MD Executive in 2012             &               & -0.27$^{***}$ &               & -0.11\\   
                                       &               & (0.10)        &               & (0.10)\\   
      \textbf{Comparison Group:}       &               &               &               & \\  
      Never MD                         & $\checkmark$  &               & $\checkmark$  &  \\  
      Has MD not in 2012               &               & $\checkmark$  &               & $\checkmark$\\   
       \\
      Observations                     & 4,095         & 1,883         & 4,083         & 1,880\\  
      \bottomrule
   \end{tabular}
\end{table}

>>>>

\begin{table}[ht!]
   \caption{\label{tab:MD_noMD_readmort_decomp_fullsample} Decomposition of Readmission and Mortality Regression Results}
   \bigskip
   \centering
   \begin{tabular}{lcccc}
      \toprule
       & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate}\\
                                   & (1)           & (2)           & (3)           & (4)\\  
      \midrule 
      Ever MD Exec x Post Programs & -0.03         &               & -0.02         &   \\   
                                   & (0.07)        &               & (0.07)        &   \\   
      MD Exec in 2012              &               & -0.27$^{***}$ &               & -0.11\\   
                                   &               & (0.10)        &               & (0.10)\\   
      \textbf{Comparison Group:}   &               &               &               & \\  
      Never MD                     & $\checkmark$  &               & $\checkmark$  &  \\  
      Has MD not in 2012           &               & $\checkmark$  &               & $\checkmark$\\   
       \\
      Observations                 & 4,095         & 1,883         & 4,083         & 1,880\\  
      \bottomrule
   \end{tabular}

   \par \raggedright 
   Results from Equation \ref{eq:decomp} with readmission and mortality rates as outcome variables.\\
   Standard errors are clustered at the hospital level.\\
   Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1
\end{table}

### 2024-05-01 Tables/MD_noMD_readmort_decomp_synth.tex
Update tables AGAIN

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality for Nonprofits Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Executive x Post 2012 & 0 &  & -0.06 & \\
 & (0.07) &  & (0.06) & \\
2012 MD Executive x Post 2012 &  & -0.19$^{*}$ &  & -0.1\\
 &  & (0.09) &  & (0.09)\\
 &  &  & & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3925 & 1845 & 3910 & 1840\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Exec x Post Programs & 0 &  & -0.06 & \\
 & (0.06) &  & (0.06) & \\
2012 MD Exec x Post Programs &  & -0.19$^{*}$ &  & -0.1\\
 &  & (0.09) &  & (0.08)\\
 &  &  &  & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3925 & 1845 & 3910 & 1840\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{5}{l}{outcome variables.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\end{tabular}
\end{table}

### 2024-05-01 Tables/MD_noMD_uncompCMI_decomp_synth.tex
Update tables AGAIN

\caption{\label{tab:MD_noMD_uncompCMI_decomp_synth}Decomposition of Uncompensated Care and CMI for Nonprofits Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Uncompensated Care} & \multicolumn{2}{c}{Case Mix Index} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Executive x Post 2012 & 0.01 &  & 0.01$^{*}$ & \\
 & (0.01) &  & (0) & \\
2012 MD Executive x Post 2012 &  & -0.03 &  & 0.01\\
 &  & (0.03) &  & (0.01)\\
 &  &  &  \vphantom{1} & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 1195 & 635 & 3015 & 1595\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_uncompCMI_decomp_synth}Decomposition of Uncompensated Care and CMI Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccc}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Uncompensated Care} & \multicolumn{2}{c}{Case Mix Index} \\
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Exec x Post 2012 & 0.01 &  & 0.01$^{*}$ & \\
 & (0.01) &  & (0) & \\
2012 MD Exec x Post 2012 &  & -0.03 &  & 0.01\\
 &  & (0.03) &  & (0.01)\\
 &  &  &  & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 1195 & 635 & 3015 & 1595\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} Results from Equation with readmission and mortality rates as}\\
\multicolumn{5}{l}{outcome variables.}\\
\multicolumn{5}{l}{\textsuperscript{} Standard errors are clustered at the hospital level.}\\
\multicolumn{5}{l}{\textsuperscript{} Signif. codes: 0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1}\\
\multicolumn{5}{l}{\textsuperscript{} Uncompensated care measured as percent of total operating expenses.}\\
\end{tabular}
\end{table}
